### 2016-09-06 R/ITHIM.Rmd
Added national ITHIM build on NHTS data
Also created future-research.org as a place to organize my thoughts on publications and so on.

tripTime <- function(data, mode = "walk"){
 return(sum(subset(data, AT == mode)$TRVLCMIN, na.rm = TRUE))
}

reformatData <- function(data){
foo <- matrix(unlist(data), nrow = 7, ncol = 2)
foo <- rbind( c(0.1, 0.1), foo)
dimnames(foo) <- list(paste0("ageClass",1:8), c("F","M"))
return(foo[,c("M","F")])
}
```

@@

```{r summary, fig.width = 20, fig.height = 10, eval = TRUE, echo = FALSE}
summary(with(subset(NHTS.trips, AT == "walk"), TRPMILES))
summary(with(subset(NHTS.trips, AT == "cycle"), TRPMILES))
summary(with(subset(NHTS.trips, AT == "other"), TRPMILES))
summary(with(subset(NHTS.trips, AT == "walk"), TRVLCMIN))
summary(with(subset(NHTS.trips, AT == "cycle"), TRVLCMIN))
summary(with(subset(NHTS.trips, AT == "other"), TRVLCMIN))

walkHours <- with(subset(NHTS.trips, {
    AT == "walk" & TRPMILES < 10 & TRPMILES/TRVLCMIN*60 < 8 & TRVLCMIN > 5 #& TRPMILES/TRVLCMIN*60 > 0.5
}), TRVLCMIN/60)

walkMiles <- with(subset(NHTS.trips, {
    AT == "walk" & TRPMILES < 10 & TRPMILES/TRVLCMIN*60 < 8 & TRVLCMIN > 5 #& TRPMILES/TRVLCMIN*60 > 0.5
}), TRPMILES)

cycleHours <- with(subset(NHTS.trips, {
      AT == "cycle" & TRPMILES < 25 & TRPMILES/TRVLCMIN*60 < 25 & TRVLCMIN > 5 #& TRPMILES/TRVLCMIN*60 > 1
}), TRVLCMIN/60)

cycleMiles <- with(subset(NHTS.trips, {
      AT == "cycle" & TRPMILES < 25 & TRPMILES/TRVLCMIN*60 < 25 & TRVLCMIN > 5 #& TRPMILES/TRVLCMIN*60 > 1
}), TRPMILES)

@@

#### Split into strata by region

```{r split, eval = TRUE, echo = FALSE}
listOfLists <- lapply(split(NHTS, NHTS$HHS),function(x) lapply(split(x, x$SEX), function(x) split(x, x$AGE)))
```

@@

```{r count, eval = TRUE, echo = FALSE}
counts <- lapply(listOfLists, function(x) lapply(x, function(x) lapply(x, countPeople)))
walkLength <- lapply(listOfLists, function(x) lapply(x, function(x) lapply( x, tripTime, mode = "walk")))
cycleLength <- lapply(listOfLists, function(x) lapply(x, function(x) lapply( x, tripTime, mode = "cycle")))
countMatrix <- lapply(counts, reformatData)
walkMatrix <- lapply(walkLength, reformatData)
cycleMatrix <- lapply(cycleLength, reformatData)
meanWalkList <- mapply(walkMatrix,   countMatrix, FUN = function(x,y) x/y*7, SIMPLIFY = FALSE)
meanCycleList <- mapply(cycleMatrix, countMatrix, FUN = function(x,y) x/y*7, SIMPLIFY = FALSE)
RwtList <- lapply( meanWalkList, function(x) ifelse(x == 0, 0.01, x) )
RctList <- lapply( meanCycleList, function(x) ifelse(x == 0, 0.01, x) )
RwtList <- lapply( RwtList, function(x) x/x[3,2] )
RctList <- lapply( RctList, function(x) x/x[3,2] )
muwtList <- lapply( meanWalkList, function(x) x[3,2] )
muctList <- lapply( meanCycleList, function(x) x[3,2] )
```

@@

for( muNonTravel in seq(1,75,length.out = 20) ){

@@

  ITHIM.national <- createITHIM(vision = "baseline", region = "national")
  ITHIM.national <- updateITHIM(ITHIM.national, "muNonTravel", muNonTravel)
  ITHIM.national <- updateITHIM(ITHIM.national, "muwt", 49.63)
  ITHIM.national <- updateITHIM(ITHIM.national, "muct", 2.50)
  DALYs <- lapply(ITHIMList, sumDALY, ITHIM.baseline = ITHIM.national)
  DALYs <- data.frame(HHS = names(DALYs), muNonTravel = muNonTravel, DALY = unlist(DALYs))
  DALYsTotal <- rbind(DALYsTotal, DALYs)
}
}else{
DALYsTotal <- readRDS(file = "./data/DALYsTotal.rds")
}
p <- ggplot(DALYsTotal, aes(x = muNonTravel, y = DALY, colour = HHS))
p  + geom_line() + theme_bw() + scale_x_discrete(name="Non-Travel METs mean") + scale_y_continuous(name="Change in DALY (National)") + facet_grid(. ~ HHS)
```

>>>>

tripTime <- function(data, mode = "walk"){
 return(sum(subset(data, AT == mode)$TRVL_MIN, na.rm = TRUE))
}

reformatData <- function(data){
foo <- matrix(unlist(data), nrow = 7, ncol = 2)
foo <- rbind( c(0.1, 0.1), foo)
dimnames(foo) <- list(paste0("ageClass",1:8), c("F","M"))
return(foo[,c("M","F")])
}

reformatData2 <- function(data){
foo <- matrix(unlist(data), nrow = 7, ncol = 2)
foo <- rbind( c(0.1, 0.1), foo)
dimnames(foo) <- list(paste0("ageClass",1:8), c("F","M"))
return(foo[,c("M","F")])
}

@@

```{r summary, fig.width = 20, fig.height = 10, eval = TRUE, echo = FALSE}
summary(with(subset(NHTS.trips, AT == "walk"), TRPMILES))
summary(with(subset(NHTS.trips, AT == "cycle"), TRPMILES))
summary(with(subset(NHTS.trips, AT == "other"), TRPMILES))
summary(with(subset(NHTS.trips, AT == "walk"), TRVL_MIN))
summary(with(subset(NHTS.trips, AT == "cycle"), TRVL_MIN))
summary(with(subset(NHTS.trips, AT == "other"), TRVL_MIN))

walkHours <- with(subset(NHTS.trips, {
    AT == "walk" & TRPMILES < 10 & TRPMILES/TRVL_MIN*60 < 8 & TRVL_MIN > 5 #& TRPMILES/TRVL_MIN*60 > 0.5
}), TRVL_MIN/60)

walkMiles <- with(subset(NHTS.trips, {
    AT == "walk" & TRPMILES < 10 & TRPMILES/TRVL_MIN*60 < 8 & TRVL_MIN > 5 #& TRPMILES/TRVL_MIN*60 > 0.5
}), TRPMILES)

cycleHours <- with(subset(NHTS.trips, {
      AT == "cycle" & TRPMILES < 25 & TRPMILES/TRVL_MIN*60 < 25 & TRVL_MIN > 5 #& TRPMILES/TRVL_MIN*60 > 1
}), TRVL_MIN/60)

cycleMiles <- with(subset(NHTS.trips, {
      AT == "cycle" & TRPMILES < 25 & TRPMILES/TRVL_MIN*60 < 25 & TRVL_MIN > 5 #& TRPMILES/TRVL_MIN*60 > 1
}), TRPMILES)

@@

#### Compute Natioal Metro Average

```{r natl}
listOfLists <- lapply(split(NHTS, NHTS$SEX),function(x) split(x, x$AGE))
counts <- lapply(listOfLists, function(x) lapply(x, countPeople))
walkLength <- lapply(listOfLists, function(x) lapply( x, tripTime, mode = "walk"))
cycleLength <- lapply(listOfLists, function(x) lapply( x, tripTime, mode = "cycle"))

countMatrix <- reformatData(counts)
walkMatrix <- reformatData(walkLength)
cycleMatrix <- reformatData(cycleLength)

meanWalkList <- walkMatrix/countMatrix*7
meanCycleList <- cycleMatrix/countMatrix*7

RwtList <- ifelse(meanWalkList == 0, 1e-4, meanWalkList)
RctList <- ifelse(meanCycleList == 0, 1e-4, meanCycleList)

RwtNational <- RwtList/RwtList[3,2]
RctNational <- RctList/RctList[3,2]
muwtNational <- meanWalkList[3,2]
muctNational <- meanCycleList[3,2]

rm("listOfLists","counts","walkLength","cycleLength","countMatrix","walkMatrix","cycleMatrix","meanWalkList","meanCycleList","RwtList","RctList","muwtList","muctList")
```

@@

```{r count, eval = TRUE, echo = FALSE}
listOfLists <- lapply(split(NHTS, NHTS$HHS),function(x) lapply(split(x, x$SEX), function(x) split(x, x$AGE)))
counts <- lapply(listOfLists, function(x) lapply(x, function(x) lapply(x, countPeople)))
walkLength <- lapply(listOfLists, function(x) lapply(x, function(x) lapply( x, tripTime, mode = "walk")))
cycleLength <- lapply(listOfLists, function(x) lapply(x, function(x) lapply( x, tripTime, mode = "cycle")))
countMatrix <- lapply(counts, reformatData)
walkMatrix <- lapply(walkLength, reformatData)
cycleMatrix <- lapply(cycleLength, reformatData)
meanWalkList <- mapply(walkMatrix,   countMatrix, FUN = function(x,y) x/y*7, SIMPLIFY = FALSE)
meanCycleList <- mapply(cycleMatrix, countMatrix, FUN = function(x,y) x/y*7, SIMPLIFY = FALSE)
RwtList <- lapply( meanWalkList, function(x) ifelse(x == 0, 1e-4, x) )
RctList <- lapply( meanCycleList, function(x) ifelse(x == 0, 1e-4, x) )
RwtList <- lapply( RwtList, function(x) x/x[3,2] )
RctList <- lapply( RctList, function(x) x/x[3,2] )
muwtList <- lapply( meanWalkList, function(x) x[3,2] )
muctList <- lapply( meanCycleList, function(x) x[3,2] )
```

@@

for( muNonTravel in seq(1,75,length.out = 3) ){

@@

  ITHIM.national <- createITHIM(vision = "baseline", region = "national")
  ITHIM.national <- updateITHIM(ITHIM.national, "muNonTravel", muNonTravel)
  ITHIM.national <- updateITHIM(ITHIM.national, "muwt", muwtNational)
  ITHIM.national <- updateITHIM(ITHIM.national, "muct", muctNational)
  ITHIM.national <- updateITHIM(ITHIM.national, "Rwt", RwtNational)
  ITHIM.national <- updateITHIM(ITHIM.national, "Rct", RctNational)
  DALYs <- lapply(ITHIMList, sumDALY, ITHIM.baseline = ITHIM.national)
  DALYs <- data.frame(HHS = names(DALYs), muNonTravel = muNonTravel, DALY = unlist(DALYs))
  DALYsTotal <- rbind(DALYsTotal, DALYs)
}
}else{
DALYsTotal <- readRDS(file = "./data/DALYsTotal.rds")
}
p <- ggplot(DALYsTotal, aes(x = muNonTravel, y = DALY, colour = HHS))
p  + geom_line() + theme_bw() + scale_x_discrete(name="Non-Travel METs mean") + scale_y_continuous(name="Change in DALY (National)") + facet_grid(. ~ HHS)
```
